---
title: "ggplot basic"
output: 
  html_document: 
    keep_md: yes
    number_sections: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# ggplot basic

## Load `ggplot2` library as a part of `tidyverse`
```{r cars}
library(tidyverse)
```

## Example data table
```{r}
diamonds %>% head
```

## `ggplot` function

- First argument: data frame
- Second argument: `aes()`

```{r}
ggplot(diamonds, aes())
```

# With `x` in `aes()` in `ggplot()`

```{r}
ggplot(diamonds, aes(x=price))
```

## `geom_hist()`: histogram

```{r}
ggplot(diamonds, aes(x=price)) + geom_histogram()
```

### new line can be inserted after `+`

```{r}
ggplot(diamonds, aes(x=price)) +
  geom_histogram()
```



## `geom_density()`: density plot

```{r}
ggplot(diamonds, aes(x=price)) +
  geom_density()
```

# With `x` and `y` in `aes()` in `ggplot()`

```{r}
ggplot(diamonds, aes(x=table, y=price))
```

## `geom_point`: Scatter plot

```{r}
ggplot(diamonds, aes(x=table, y=price)) + 
  geom_point()
```

### Change size of points in scatter plot

```{r}
ggplot(diamonds, aes(x=table, y=price)) + 
  geom_point(size = 0.5)
```

## `geom_smooth`: Draw smoothed line

```{r}
ggplot(diamonds, aes(x=depth, y=price)) + 
  geom_smooth()
```

### `geom_point()` + `geom_smooth`

```{r}
ggplot(diamonds, aes(x=table, y=price)) + 
  geom_point(size = 0.5) +
  geom_smooth()
```


## `geom_bin2d()`

```{r}
ggplot(diamonds, aes(x=table, y=price)) + 
  geom_bin2d()
```

## `geom_boxplot()`: box plot

```{r}
ggplot(diamonds, aes(x=clarity, y=price)) + 
  geom_boxplot()
```

## `geom_violin()`: violin plot

```{r}
ggplot(diamonds, aes(x=clarity, y=price)) + 
  geom_violin()
```


# sessionInfo()

```{r}
sessionInfo()
```
