---
title: "ggplot facet"
output: 
  html_document: 
    keep_md: yes
    number_sections: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# ggplot basic

## Load `ggplot2` library as a part of `tidyverse`
```{r cars}
library(tidyverse)
```

## Example data table
```{r}
diamonds %>% head
```

## `ggplot` function

- First argument: data frame
- Second argument: `aes()`

```{r}
ggplot(diamonds, aes())
```

# With `x` in `aes()` in `ggplot()`

## `geom_hist()`: histogram

```{r}
ggplot(diamonds, aes(x=price)) +
  geom_histogram()
```

## `+ facet_wrap()`

```{r}
ggplot(diamonds, aes(x=price)) +
  geom_histogram() +
  facet_wrap(~color)
```


```{r}
ggplot(diamonds, aes(x=price)) +
  geom_histogram() +
  facet_wrap(~cut)
```

## `scales` option in `facet_wrap()`


```{r}
ggplot(diamonds, aes(x=price)) +
  geom_histogram() +
  facet_wrap(~cut, scales = "free_y")
```

## `+ facet_grid()`

```{r}
ggplot(diamonds, aes(x=price)) +
  geom_histogram() +
  facet_grid(cut~color)
```

## `scales` option in `facet_grid()`

```{r}
ggplot(diamonds, aes(x=price)) +
  geom_histogram() +
  facet_grid(cut~color, scales = "free_y")
```

## `geom_density()` + `facet_wrap()`

You can try!


# With `x` and `y` in `aes()` in `ggplot()`

```{r}
ggplot(diamonds, aes(x=table, y=price))
```

## `geom_point`: Scatter plot

```{r}
ggplot(diamonds, aes(x=table, y=price)) + 
  geom_point(size = 0.5)
```

## + `facet_wrap()`

```{r}
ggplot(diamonds, aes(x=table, y=price)) + 
  geom_point(size = 0.5) + 
  facet_wrap(~cut)
```


## `geom_point()` + `geom_smooth` + `facet_wrap()`

```{r}
ggplot(diamonds, aes(x=table, y=price)) + 
  geom_point(size = 0.5) +
  geom_smooth() +
  facet_wrap(~cut)
```


## `geom_boxplot()`: box plot

```{r}
ggplot(diamonds, aes(x=clarity, y=price)) + 
  geom_boxplot()
```

## + `facet_wrap()`

```{r}
ggplot(diamonds, aes(x=clarity, y=price)) + 
  geom_boxplot() + 
  facet_wrap(~color)
```


# sessionInfo()

```{r}
sessionInfo()
```
