---
title: "plot_grid() in cowplot"
output: 
  html_document: 
    keep_md: yes
    number_sections: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Basics

## Load `ggplot2` and `cowplot` libraries as a part of `tidyverse`
```{r cars}
library(tidyverse)
library(cowplot)
```

## Example data table
```{r}
iris %>% head
```

# example plot
```{r}
ggplot(iris, aes(x = Species, y = Sepal.Length)) +
  geom_boxplot() + theme_bw() +
  theme(axis.text.x = element_text(size = 14, angle = 90, vjust = 0.5))
```

## plot can be assigned to an object

```{r}
p1 <- ggplot(iris, aes(x = Species, y = Sepal.Length)) +
  geom_boxplot() + theme_bw() +
  theme(axis.text.x = element_text(size = 14, angle = 90, vjust = 0.5))
```

# Example plot 2

```{r}
ggplot(iris, aes(x = Sepal.Length, fill = Species)) +
  geom_density(alpha = 0.7) + theme_bw() +
  theme(legend.position = c(0.8, 0.8))
```

## plot can be assigned to an object

```{r}
p2 <- ggplot(iris, aes(x = Sepal.Length, fill = Species)) +
  geom_density(alpha = 0.7) + theme_bw() +
  theme(legend.position = c(0.8, 0.8))
```

# `plot_grid()`

```{r}
plot_grid(p1, p2)
```

## `labels` option in  `plot_grid()`

```{r}
plot_grid(p1, p2, labels = "AUTO")
```

```{r}
plot_grid(p1, p2, labels = "auto")
```

```{r}
plot_grid(p1, p2, labels = c("A1", "A2"))
```


## `align` option in `plot_grid()`

```{r}
plot_grid(p1, p2, labels = "AUTO")
```

```{r}
plot_grid(p1, p2, labels = "AUTO", align = "h")
```

## label settings

```{r}
plot_grid(p1, p2, labels = "AUTO", align = "h",
          label_size = 10,
          label_fontfamily = "serif",
          label_fontface = "plain",
          label_colour = "blue")
```

## `ncol` option

```{r}
plot_grid(p1, p2, labels = "AUTO", ncol = 1)
```

## `rel_widths` option

```{r}
plot_grid(p1, p2, labels = "AUTO", rel_widths = c(1, 2))
```


## Complex layout

```{r}
plot_grid(
  p1, NULL, NULL, p2,
  labels = "AUTO", ncol = 2
)
```

# Nested plot grids

```{r}
bottom_row <- plot_grid(p1, p2, labels = c('B', 'C'), label_size = 12)
p3 <- ggplot(mtcars, aes(x = qsec, y = disp)) + geom_point() + facet_wrap(~gear)

plot_grid(p3, bottom_row, labels = c('A', ''), label_size = 12, ncol = 1)
```

## `align_plots()`

```{r}
plots <- align_plots(p3, p1, align = 'v', axis = 'l')
# then build the bottom row
bottom_row <- plot_grid(plots[[2]], p2, labels = c('B', 'C'), label_size = 12)

# then combine with the top row for final plot
plot_grid(plots[[1]], bottom_row, labels = c('A', ''), label_size = 12, ncol = 1)
```


# Joint plot titles

```{r}
# now add the title
plot_row <- plot_grid(p1, p2)

title <- ggdraw() + 
  draw_label(
    "Miles per gallon decline with displacement and horsepower",
    fontface = 'bold',
    x = 0,
    hjust = 0
  ) +
  theme(
    # add margin on the left of the drawing canvas,
    # so title is aligned with left edge of first plot
    plot.margin = margin(0, 0, 0, 7)
  )
plot_grid(
  title, plot_row,
  ncol = 1,
  # rel_heights values control vertical title margins
  rel_heights = c(0.1, 1)
)
```

# sessionInfo()

```{r}
sessionInfo()
```

# References

- https://wilkelab.org/cowplot/articles/plot_grid.html
